%%!Mode:: "Tex:UTF-8"
\bibliographystyle{unstr}
\begin{thebibliography}{99}\addtolength{\itemsep}{-2.5ex}\setlength{\itemsep}{0cm}
\zihao{5}
\bibitem{2}{S. H. Strogatz. Exploring complex networks [J]. Nature, 2001, 410: 268-276.}
\bibitem{0}{A. Barabasi, R. Albert. Emergence of scaling in random networks[J]. Science, 1999, 286(5439): 509-512.}
%\bibitem{1}{毕桥, 方锦清. 网络科学与统计物理方法[M]. 北京:北京大学出版社, 2011: 1-13.}

\bibitem{4}{周涛, 柏文洁, 汪秉宏, 刘之景, 严钢. 复杂网络研究概述[J]. 物理, 2005, 34: 31-36.}
\bibitem{5}{赵明,周涛,陈关荣,汪秉宏.复杂网络上动力系统同步的研究进展―如何提高网络的同步能力[J]. 物理学进展, 2008, 28(1): 22-34. }
%/----------------------------application----------------------------------------------------------/
\bibitem{6}{方锦清. 驾驭强流束晕与探索网络科学[M]. 原子能出版社, 2008:1-22, 215-265.}
\bibitem{7}{汪小帆, 李翔, 陈关荣. 复杂网络理论及其应用[M]. 北京: 清华大学出版社, 2006: 1-16, 194-243.}
\bibitem{8}{V. N. Belykh, I. V. Belykh,  M. Erik. Cluster synchronization modes in an ensemble of coupled chaotic oscillators [J]. Physical Review E, 2001, 3(036216): 1-4.}
\bibitem{9}{F. X. Wang, G. R. Chen. Synchronization in scale-free dynamical networks: robustness and fragility[J]. IEEE Trans. Circuits Syst. I, 2002, 49(1): 54-62.}
\bibitem{10}{ L. M. Pecora, T. L. Carroll. Synchronization in chaotic systems[J]. Physical Review Letters, 1990, 64(8):821-824.}
\bibitem{15}{ M. D. Vieira. Chaos and synchronized chaos in an earthquake model[J]. Phys. Rev. Lett., 1999, 82, 201-204.}
\bibitem{16}{S.~Wang, J.~Kuang, J.~Li, Y.~Luo, H.~Lu, G.~Hu. Chaos-based secure communications in a large community[J]. Phys. Rev. E, 2002, 66, 065202.}
\bibitem{17}{L. Kunbert, K. I. Agladze, V. I. Krinsky. Image processing using light-sensitive chemical waves[J]. Nature, 1989, 337, 244-247.}
%/-----------------------------------network---------------------------------------------------/
\bibitem{11}{王小帆, 苏厚胜. 复杂动态网络控制研究进展[J]. 力学进展, 2008, 38(6): 751-765.}
\bibitem{12}{吕金虎. 复杂网络的同步：理论、方法、应用与展望[J]. 力学进展, 2008, 38(6): 713-722.}
\bibitem{13}{X. Li, X. F. Wang, G. R. Chen. Pingning a complex dynamical network to its equilibrium[J]. IEEE Transactions on Circuits and Systems-I. 2004, 51(10): 2074-2087.}
\bibitem{14}{S. H. Strogatz, I. Stewart. Coupled oscillators and biological synchronization[J]. Sci. Amer.,1993, 269(6): 102-109.}

\bibitem{genesyn}{A. Arenas, A. D{\'{i}}az-Guilera, J. Kurths, Y. Moreno, C. Zhou. Synchronization in complex networks[J]. Chaos, 2008, 18(3): 2183-2185.}

\bibitem{finitetimesyn}{W. Cui, S. Sun, J. Fang, Y. Xu, L. Zhao. Finite-time synchronization of Markovian jump complex networks
with partially unknown transition rates[J]. Journal of the Franklin Institute, 2014, 351, 2543–2561.}



\bibitem{fixsyn}{Y. Zhou, C. Sun. Fixed time synchronization of complex dynamical networks[C]. 2015, 中国智能自动化学术会议, 105:649–655.}

%\bibitem{19}{Z. Wang, Y. Wang, Y. Liu. Global Synchronization for discrete-time stochastic complex networks with randomly occurred nonlinearities and mixed time delays[J]. IEEE Transactions on Neural Networks, 2010, 21(1):11-25.}
%
%\bibitem{18}{C. G. Li, G. R. Chen. Synchronization in general complex dynamical networks with coupling delays[J]. Physica A, 2004, 343: 263-278.}

\bibitem{abssyn}{M. Zhan, X. G. Wang, X. F. Gong, G. W. Wei, C. H. Lai. Complete synchronization and generalized synchronization of
one-way coupled time-delay systems[J]. Phys Rev E, 2003, 68, 036208.}

\bibitem{clusyn}{H. Dong, D. Ye, J. Feng, J. wang. Almost sure cluster synchronization of {M}arkovian switching complex networks with stochastic noise via decentralized adaptive pinning control[J]. Nonlinear Dynamics, 2016:1-13.}

\bibitem{phasyn}{C. Li, G. Chen. Phase synchronization in small-world networks of chaotic oscillators[J]. Physica A, 2004, 341: 73-79.}

\bibitem{23}{X. M. Feng, F. Q. Zhang, W. J. Wang. Global exponential synchronization of delayed fuzzy cellular neural networks with
impulsive effects[J]. Chaos, 2011, 44: 1-3, 9-16.}

%\bibitem{24}{C. Hu, J. Yu, H. J. Jiang, Z. D. Teng. Exponential lag synchronization for neural networks with mixed delays via periodically
%intermittent control[J]. Chaos, 2010, 20, 023108: 1-8.}



%\bibitem{p24}{T. Chen, X. Liu, W. Lu. Pinning complex networks by a single controller. IEEE Transactions on Circuits and Systems-1: Regular Papers, 2007, 54(6):1317–1326.}
%\bibitem{p25}{Q. Xie and G. Chen. Synchronization on complex networks of networks. IEEE Trans. Neural. Netw. Learn, 2014, 25: 2110–2118.}
%\bibitem{p26}{Q. Xie and G. Chen. Synchronization in complex networks under structural evolu-tion. Franklin Inst, 2014, 351: 358–372.}
%\bibitem{p27}{Z. Zhang and G. Hu. Global synchronization of complex networks with interval time-varying delays and stochastic disturbances. International Journal of Computer Mathematics, 2011, 88:249–264.}
%\bibitem{p28}{M. Rosenblum, A. Pikovsky and J. Kurths. Phase synchronization of chaotic os-cillators. Phys. Rev. Lett, 1996, 76:1804–1807.}
%\bibitem{p29}{Y. Wang and J. Cao. Cluster synchronization in nonlinearly coupled delayed networks of non-identical dynamic systems. Nonlinear Analysis: Real World Applica-tion, 2013, 14:842–851.}

\bibitem{Karimi5}
H.~Karimi and P.~Maass.
\newblock Delay-range-dependent exponential {$H_\infty$} synchronization of a
  class of delayed neural networks.
\newblock {\em Chaos Solitons \& Fractals}, 41(3):1125--1135, 2009.

\bibitem{Multi6}
Y.~Tang, Z.~Wang, W.~Wong, J.~Kurths, and J.~Fang.
\newblock Multiobjective synchronization of coupled systems.
\newblock {\em Chaos}, 21(2):939--952, 2011.

\bibitem{Lu7}
J.~Lu, D.~Ho, J.~Cao, and J.~Kurths.
\newblock Exponential synchronization of linearly coupled neural networks with
  impulsive disturbances.
\newblock {\em IEEE Transactions on Neural Networks}, 22(2):329--36, 2011.

\bibitem{Liu8}
Y.~Liu, Z.~Wang, J.~Liang, and X.~Liu.
\newblock Synchronization and state estimation for discrete-time complex
  networks with distributed delays.
\newblock {\em IEEE Transactions on Systems Man \& Cybernetics Part B
  Cybernetics}, 38(5):1314--25, 2008.

\bibitem{Karimi10}
H.~Karimi, M.~Zapateiro, and N.~Luo.
\newblock Adaptive synchronization of master-slave systems with mixed neutral
  and discrete time-delays and nonlinear perturbations.
\newblock {\em Asian Journal of Control}, 14(1):251--257, 2012.

\bibitem{Lu9}
J.~Lu, D.~Ho, and Z.~Wang.
\newblock Pinning stabilization of linearly coupled stochastic neural networks
  via minimum number of controllers.
\newblock {\em IEEE Transactions on Neural Networks}, 20(10):1617--29, 2009.

\bibitem{Turci11}
L.~Turci, P.~Lellis, E.~Macau, M.~Bernardo, and M.~Sim{\"{o}}es.
\newblock Adaptive pinning control: A review of the fully decentralized
  strategy and its extensions.
\newblock {\em European Physical Journal Special Topics}, 223(13):2649--2664,
  2014.

\bibitem{Jin12}
J.~Zhou, J.~Lu, and J.~L{\"{u}}.
\newblock Pinning adaptive synchronization of a general complex dynamical
  network.
\newblock {\em Automatica}, 45(4):996--1003, 2008.

\bibitem{Turci13}
L.~Turci and E.~Macau.
\newblock Adaptive node-to-node pinning synchronization control of complex
  networks.
\newblock {\em Chaos}, 22(3):361--383, 2012.

\bibitem{Li15}
Z.~Li, H.~Park, , and Z.~Wu.
\newblock Synchronization of complex networks with nonhomogeneous {M}arkov jump
  topology.
\newblock {\em Nonlinear Dynamics}, 74(1-2):65--75, 2013.

\bibitem{p10Markovian}
Y.~Ma and Y.~Zheng.
\newblock Synchronization of continuous-time {M}arkovian jumping singular
  complex networks with mixed mode-dependent time delays.
\newblock {\em Neurocomputing}, 156:52--59, 2015.

\bibitem{p11Markovian}
Y.~Han, W.~Lu, Z.~Li, and T.~Chen.
\newblock Pinning dynamic systems of networks with {M}arkovian switching
  couplings and controller node set.
\newblock {\em Systems \& Control Letters}, 65(1):56--63, 2014.

\bibitem{M18} X. Yang, J. Cao, and J. Lu. Synchronization of Markovian coupled neural networks with nonidentical node-delays and random coupling strengths. IEEE Transac-tions on Neural Networks and Learning Systems, 23(1):60-71,2012.
\bibitem{mm19} Y.C.Ma, Y.Q.Zheng, Synchronization of continuous time Markovian jumping singular complex networks with mixed mode-dependent time delays, Neurocomput-ing156: 52-59, 2015.
\bibitem{M20} Z. Li, J Park, Z Wu, Synchronization of complex networks with nonhomogeneous Markov jump topology, Nonlinear Dynamics 74: 65-75, 2013.
\bibitem{M21} X. Liu, H1 cluster synchronization for a class of neutral complex dynamical networks with Markovian switching, The Scientic World Journal, 1-20, 2014.
\bibitem{M22} X. Yang, J. Cao, Adaptive pinning synchronization of complex networks with stochastic perturbations, Discrete Dynamics in Nature and Society, 179-186, 2010.
\bibitem{M23} X. Zhou, K. Luo, Cluster synchronization of stochastic complex networks with Markovian switching and time-varying delay via impulsive pinning control, Discrete Dynamicsin Nature and Society, 1-9, 2014.
\bibitem{M24} J. Wang, M. Kwong, F. Austin, Mean-square exponential synchronization of Markovian switching stochastic complex networks with time-varying delays by pin-ning control, Abstract and Applied Analysis, 919-929, 2012.
\bibitem{M25} X. Wang, J. Fang, A. Dai, W. Cui, G. He, Mean square exponential synchronization for a class of Markovian switching complex networks under feedback control and M-matrix approach, Neurocomputing, 144, 357-366, 2014.


\bibitem{M17} S. Hao , J. Park, W. Guang and Z. Qiang . Finite-time synchronization for complex networks with semi-Markov jump topology. Communications in Nonlinear Science and Numerical Simulation, 24: 40–51, (2015).

\bibitem{X18}
X.~Yang, J.~Cao, and J.~Lu.
\newblock Synchronization of randomly coupled neural networks with {M}arkovian
  jumping and time-delay.
\newblock {\em IEEE Transactions on Circuits \& Systems I Regular Papers},
  60(2):363--376, 2013.
\bibitem{M19}
M.~Baumeister, J.~Bühren, and T.~Kohnen.
\newblock Adaptive synchronization in an array of chaotic neural networks with
  mixed delays and jumping stochastically hybrid coupling.
\newblock {\em Communications in Nonlinear Science \& Numerical Simulation},
  14(9-10):3615--3628, 2009.

\bibitem{randomcoupling1}
X.~Yang, J.~Cao, and J.~Lu.
\newblock Synchronization of {M}arkovian coupled neural networks with
  nonidentical node-delays and random coupling strengths.
\newblock {\em IEEE Transactions on Neural Networks and Learning Systems}, 23,
  2012.

\bibitem{Eventmultiagentnoises}
A.~Hu, J.~Cao, M.~Hua, and L.~Guo.
\newblock Event-triggered consensus of multi-agent systems with noises.
\newblock {\em Franklin Institute}, 352:3489--3503, 2015.

\bibitem{p29}{X. Yang, J. Cao, and J. Lu, Synchronization of delayed complex dynamical networks with impulsive and stochastic effects. Nonlin. Anal.: Real World Appl., 12(4): 2252–2266, 2011.}

\bibitem{p30}{W. Yu and J. Cao, Synchronization control of stochastic delayed neural networks, Phys. A, 373(1):252–260,2007.}

\bibitem{p31}{X. Yang, J. Cao, Y. Long, and W. Rui, Adaptive lag synchronization for competi-tive neural networks with mixed delays and uncertain hybrid perturbations, IEEE Trans. Neural Netw., 21(10):1656–1667,2010.}

\bibitem{p32}{A. Hu and J. Cao and M. Hu and L. Guo, Cluster synchronization in directed networks of non-identical systems with noise via random pinning control, Physica A, 395,537-548,2014.}

\bibitem{natsyn}{X. F. Wang. Complex networks: topology, dynamics and synchronization, Int. J. Bifurcat. Chaos, 2002, 12(5):885-916.}

\bibitem{pin1}
J.~Lu, D.~Ho, and Z.~Wang.\newblock Pinning stabilization of linearly coupled stochastic neural networks via minimum number of controllers.\newblock {\em IEEE Transactions on Neural Networks}, 20(10):1617--29, 2009.
\bibitem{pin2}J.~Zhou, J.~Lu, and J.~L{\"{u}}.\newblock Pinning adaptive synchronization of a general complex dynamical network.\newblock {\em Automatica}, 45(4):996--1003, 2008.
\bibitem{pin3}
L.~Turci and E.~Macau.\newblock Adaptive node-to-node pinning synchronization control of complex networks.\newblock {\em Chaos}, 22(3):361--383, 2012.
\bibitem{period}S.~Li, J.~Cao, and Y.~He.\newblock Pinning controllability scheme of directed complex delayed dynamical networks via periodically intermittent control.\newblock {\em Discrete Dynamics in Nature \& Society}, 2016:1--10, 2016.

\bibitem{eventmult1} A. Hu, J. Cao, M. Hua, and L. Guo. Event-triggered consensus of multi-agent systems with noises. Journal of the Franklin Institute, 352:3489–3503, 2015.
\bibitem{eventmult2} D. Dimarogonas, E. Frazzoli, and K. Johansson. Distributed-event-triggered control for multi-agent systems. IEEETrans. Automat. Control, 57:1291–1297, 2012. 5.
\bibitem{eventmult3} H. Yan, Y. Shen, H. Zhang, and H. Shi. Decentralized event-triggered consensus control for second-order multi agent systems. Neurocomputing, 133:18–24, 2014.
\bibitem{eventmult4} Y. Fan and J. Yang. Average consensus of multi-agent systems with self-triggered controllers.Neurocomputing,177:33–39, 2016.
\bibitem{eventmult5} T. Xie, X. Liao, and H. Li. Leader-following consensus in second-order mul-ti-agent systems with input time delay: An event-triggered sampling approach. Neu-rocomputing, 177:130–135, 2016.
\bibitem{eventmult6} H. Li, C. Ming, S. Shen, and W. Wong. Event-triggered control for multi-agent systems with randomly occurring nonlinear dynamics and time-varying delay. Journal of the Franklin Institute, 351:2582–2599, 2014.
\bibitem{eventmult7} D. Xie, S. Xu, Y. Chu, and Y. Zou. Event-triggered average consensus for multi-agent systems with nonlinear dynamics and switching topology. Journal of the Franklin Institute, 352:1080–1098, 2015.
\bibitem{eventmult8} H. Ma, D. Liu, D. Wang, F. Tan, and C. Li. Centralized and decentralized event-triggered control for group consensus with fixed topology in continuous time. Neurocomputing, 161:267–276, 2016.
\bibitem{eventmult9} G. S. Seyboth, D. V. Dimarogonas, and K. H. Johansson, ”Event-based broadcasting for multi-agent average consensus,” Automatica, 2013, 49(1): 245-252.

\bibitem{eventsyn1} H. Li, X. Liao, G. Chen, D. Hill, Z. Dong, and T. Huang. Event-triggered asynchronous intermittent communication strategy for synchronization in complex dy-namical networks. Neural Networks, 66:1–10, 2015.
\bibitem{eventsyn2} W. Lu, Y. Han and T. Chen. Synchronization in networks of linearly coupled dynamical systems via event-triggered diffusions. IEEE Transactions on Neural Networks and Learning Systems, page online, 2015.
\bibitem{eventsyn3} Z. Chen, D. Li, Y. Huang, and C. Tang. Event-triggered communication for time synchronization in WSNs. Neurocomputing, 177:416–426, 2016.
\bibitem{eventsyn4} B. Zhou, X. Liao, T. Huang, and G. Chen. Pinning exponential synchronization of complex networks via event triggered communication with combinational measurements. Neurocomputing, 157:199–207, 2015.
\bibitem{eventsyn5} J. Lang, Y. Zhang, and B. Zhang. Event-triggered network-based synchronization of delayed neural networks. Neurocomputing, online, 2016.
\bibitem{eventsyn6} J. Zhang, C. Peng, D. Du, and M. Zheng. Adaptive event-triggered communica-tion scheme for networked control systems with randomly occurring nonlinearities and uncertainties. Neurocomputing, 174:475–482, 2016.
\bibitem{eventsyn7} W. Lu, Y. Han, and T. Chen.Pinning networks of coupled dynamical systems with Markovian switching couplings and event-triggered diffusions.Journal of the Franklin Institute, 352, 2015.

\bibitem{eventsyn8} K. J. {\AA}ström, B. Bernhardsson. Comparison of Riemann and Lebesgue sampling for first order stochastic systems. In IEEE Conference on Decision \& Control, pages 2011–2016, 2003.
\bibitem{eventsyn9} B. Wang, X. Meng, and T. Chen. Event based pulse-modulated control of linear stochastic systems. IEEE Transactions on Automatic Control, 59(59):2144–2150, 2014.

\bibitem{ChenT_event_triggered}{W.~Lu, Y.~Han, T.~Chen, Pinning networks of coupled dynamical systems with {M}arkovian switching couplings and event-triggered diffusions[J]. Journal of the Franklin Institute, 2015, 352(): 3526--3545.}

\bibitem{packetloss} M. Guinaldo, D. Lehmann, J. S¢nchez, S. Dormido, and K. H. Johansson. Dis-tributed event-triggered control with network delays and packet-losses. In Fifty-one the IEEE Conference on Decision and Control, 1–6, Maui.
\bibitem{stoprocc}{林元烈. 应用随机过程[M]. 清华大学出版社, 2002.}
\bibitem{yitengprocc}{Steven E. Shreve 著, 陈启宏, 陈迪华 译. 金融随机分析(第二卷)[M]. 上海财经大学出版社, 2015.}
\bibitem{Kronecker}{R.~Horn, C.~Johnson, Matrix Analysis[M]. University of Alberta, 1985.}
\bibitem{leq} S. Boyd, L. Ghaoui, E. Feron, and V. Balakrishnan. Linear Matrix Inequalities in System and Control Theory. Philadelphia, PA: Soc. Ind. Appl. Math., 1994


\bibitem{pwang30}{X. Wang, H. Su. Pinning control of complex networked systems: A decade after and beyond. Annual Reviews in Control, 2014, 38: 103-111.}
\bibitem{ptang31}{Y. Tang, F. Qian, H. Gao, J.Kurths. Synchronization in complex networks and its application – A survey of recent advances and challenges. Annual Reviews in Con-trol, 2014, 38: 184-198.}
\bibitem{22}{W. Guo. Lag synchronization of complex networks via pinning control[J]. Nonlinear Anal, 2011, 12(5): 2579-2585.}
\bibitem{nonl-asym}{X.~Liu and T.~Chen. Synchronization analysis for nonlinearly-coupled complex networks with an asymmetrical coupling matrix[J].
Physica A Statistical Mechanics $\&$ Its Applications, 2008, 387:4429--4439.}

\bibitem{Gronwall}
T.~Gronwall.
\newblock Note on the derivatives with respect to a parameter of the solutions
  of a system of differential equations.
\newblock {\em Ann. Math.}, 20:292--296, 1919.
\newblock 4.

\bibitem{Bellman}
R.~Bellman.
\newblock The stability of solutions linear of differential equations.
\newblock {\em Duke Math. J.}, 10:643--647, 1943.
\newblock 4.

\bibitem{differential} X. Mao. Stability of stochastic differential equations with Markovian switching. Stochastic Processes and Their
Applications, 79:45–67, 1999.

\bibitem{chuacircuits} M. Porfiri and F. Fiorilli. Experients on node-to-node pinning control of chua’s circuits. Physica D, 239:454–464,
2010.
\bibitem{ldelay-network}{X.~Yang, J.~cao, and J.~Lu. Synchronization of delayed complex dynamical networks with impulsive and stochastic effects[J].
Nonlinear Analysis: Real World Applications, 2011, 12(4): 2252--2266.}
\bibitem{delay-inq}{X.~Liu, P.~Li, T.~Chen, Cluster synchronization for delayed complex networks via periodically intermittent pinning control[J]. Neurocomputing, 2015, 162: 191--200.}













\bibitem{20}{J. Zhou, T. P. Chen, L. Xiang. Chaotic lag synchronization of coupled delayed neural networks and its applications in
secure com-munication[J]. Circuits Syst Signal Process, 2005, 24, 5: 599-613.}
\bibitem{21}{Q. Miao, Y. Tang, S. Lu, J. Fang. Lag synchronization of a class of chaotic systems with unknown parameters[J]. Nonlinear
Dynam, 2009, 57:1-2, 107-112.}


\bibitem{25}{C. Vreeswijk. Partial synchronization in populations of pulse-coupled oscillators[J]. Phys. Rev. E, 1996, 54: 5522-5537.}
\bibitem{26}{B. Ao, Z. G. Zheng, Partial Synchronization on Complex Networks[J]. Europhys. Lett., 2009, 74(2), 50006.}
%/-----------------synchronization review------------------------------/

\bibitem{29}{ W. Xia, J. Cao. Pinning synchronization of delayed dynamical networks via periodically intermittent control[J]. Chaos. 2009, 19(1), 013120.}
\bibitem{30}{W. Yu, G. Chen, J. Lü. On pinning synchronization of complex dynamical networks[J]. Automatica. 2009, 45(2): 429-435.}
\bibitem{31}{T. Chen, X. Liu, W. Lu. Pinning complex networks by a single controller[J]. IEEE Trans. Cir. Syst. 2007, I54: 1317-1326.}
\bibitem{32}{X. Li, X. Wang, G. Chen. Pinning a complex dynamical networks to its equilibrium[J]. IEEE Trans. Cir. Syst. 2004, I51: 2074-2087.}

\bibitem{33}{张刚, 张伟. 复杂网络的脉冲同步[J]. 动力学与控制学报,2009, 7(1), 1-4.}
\bibitem{34}{C. G. Li, G. R. Chen. Synchronization in general complex dynamical networks with coupling delays[J]. Physica A, 2004, 343: 263-278.}
\bibitem{35}{P. Li, J. D. Cao, Z. D. Wang. Robust impulsive synchronization of coupled delayed neural networks with uncertainties[J]. Phys A. 2007, 373, 261-272.}
\bibitem{36}{周进, 陈天平, 高艳辉. 脉冲控制下复杂网络的同步动力学行为[A]. 第二届全国复杂动态网络学术论坛论文集[C], 2005.}


\bibitem{37}{E. Montbri, J. Kurths, B. Blasius. Synchronization of two interacting populations of oscillators[J]. Phys RevE. 2004, 70, 056125.}
\bibitem{38}{C. P. Li, W. G.~Sun, J.~Kurths. Synchronization between two coupled complex networks[J]. Phys. Rev. E, 2007, 76, 046204.}
\bibitem{39}{W. Sun, R. Wang, W. Wang, J. Cao. Analyzing inner and outer synchronization between two coupled discrete-time networks with time delays[J]. Cogn. Neurodyn. 2010, 4(3): 225-231.}
\bibitem{40}{W. Sun, Z. Z. Yan, S. H. Chen, J. H. L$\ddot{u}$. Outer Synchronization of Complex Networks by Impulse[J]. Commun. Theor. Phys. 2011, 56(5): 885–890.}
\bibitem{41}{S. Zheng. Inner-outer synchronization analysis of two complex networks with delayed and non-delayed coupling[J]. Journal
of Information and Computing Science, 2012, 7(1), 011-018.}
\bibitem{42}{曹素雯. 不同节点动态的复杂网络外部同步牵制控制[J].计算机技术与发展, 2013, 23(11), 124-128.}
\bibitem{43}{ X. J. Wu, H. T. Lu. Outer synchronization between two different fractional-order general complex dynamical networks[J]. Chin. Phys. B, 2010, 19(7), 070511.}
\bibitem{44}{P. He, C.~G. Jing, T. Fan, C. Z. Chen. Outer Synchronization of Complex Networks with Multiple CouplingTime-varying Delays[J]. International Journal of Control and Automation, 2013, 6(4): 197-216.}
\bibitem{45}{Y.~Z. Sun, W.~Li, J.~Ruan. Generalized outer synchronization between complex dynamical networks with time delay and noise perturbation[J]. Commun Nonlinear Sci Numer Simulat, 2013, 18: 989–998.}
\bibitem{46}{Z. C. Li, X. P. Xue. Outer synchronization of coupled networks using arbitrary coupling strength[J]. CHAOS, 2010, 20, 023106. }
\bibitem{47}{X. Q. Wu, W. X. Zheng, J. Zhou. Generalized outer synchronization between complex dynamical networks[J]. CHAOS, 2009, 19, 013109.}


\bibitem{48}{S. Zheng, W. Shao. Mixed outer synchronization of dynamical networks with nonidentical nodes and output coupling[J]. Nonlinear Dyn, 2013, 73: 2343-2352.}
\bibitem{49}{S. K. Bhowmick, C. Hens, D. Ghosh, S. Dana. Mixed synchronization in chaotic oscillators using scalar coupling[J]. Physics Letters A, 2012, 376: 2490–2495.}
\bibitem{50}{ J. Wei. Wang,  Q. H. Ma, L. Zeng. A novel mixed-synchronization phenomenon in coupled Chua’s circuits via non-fragile linear control[J]. Chin. Phys. B Vol. 2011, 20(8), 080506.}
\bibitem{51}{J. W. Wang, Q. H. Ma, Z. Li, S. A. E. Mohammed. Mixed outer synchronization of coupled complex networks with time-varyingcoupling delay[J]. Chaos. 2011, 21(1), 013121.}
\bibitem{52}{A. D. Dai, W. N. Zhou, J. W. Feng, J. A. Fang and S. B. Xu. Exponential synchronization of the coupling delayed switching
complex dynamical networks via impulsive control[J], Advances in Difference Equations, 2013, 195.}

\bibitem{event-triggered-consensus}{D.~Xie, S.~Xu, Y.~Chu, Y.~Zou, Event-triggered average consensus for multi-agent systems with nonlinear dynamics and switching topology[J]. Journal of the Franklin Institute, 2015, 352(3): 1080--1098.}
\end{thebibliography}




